\textbf{Case Studies II - Community Talks}

### 2013-04-09 ricardogarfe/final_report/003-plan9-community-talk.tex
Update 003-plan9-community-talk.tex

\par What is Plan9 ? A movie from Ed Wood ? A 'new' Operative System ?\textit{Plan9 from Bell Labs} is an Operative System developed \href{http://swtch.com/plan9history/}{between the 80's and 2002} by the research and development subsidiary of the French-owned Alcatel-Lucent in Berkeley Heights, New Jersey, United States.\textit{Yes, the name is from the movie :)}

@@

\par By other way, you have a very good guidelines and references by very good C developers to \href{http://plan9.bell-labs.com/magic/man2html/6/style}{develop Plan9}.

\begin{itemize}
	\item don't use // comments; some old Plan 9 code does, but we're converting it as we touch it. We do sometimes use // to comment-out a few lines of code.
	\item avoid gotos.
	\item no tabs expanded to spaces.
	\item no white space before opening braces.
	\item no white space after the word "if", "for", "while", etc.
	\item no braces around single-line blocks (e.g., if, for, and while bodies).
	\item integer-valued functions return -1 on error, 0 or positive on success.
	\item functions that return errors should set errstr(2).
	\item variable and function names are all lowercase, with no underscores.
	\item enum or \#defined constants should be Uppercase or UPPERCASE.
	\item struct tags are Uppercase, with matching typedefs.
	\item automatic variables (local variables inside a function) are never initialized at declaration.
	\item follow the standard idioms: use x$<$0 not 0$>$x, etc.
\end{itemize} The end they follow a very common development filosophy:

>>>>

\par What is Plan9 ? A movie from Ed Wood ? A 'new' Operative System ?\textit{Plan9 from Bell Labs} is an Operative System developed  \textbf {\href{http://swtch.com/plan9history/}{between the 80's and 2002}} by the research and development subsidiary of the French-owned Alcatel-Lucent in Berkeley Heights, New Jersey, United States.\textit{Yes, the name is from the movie :)}

@@

\par By other way, you have a very good guidelines and references by very good C developers to \textbf {\href{http://plan9.bell-labs.com/magic/man2html/6/style}{develop Plan9}}.

\begin{itemize}
	\item don't use // comments; some old Plan 9 code does, but we're converting it as we touch it. We do sometimes use // to comment-out a few lines of code.
	\item avoid gotos.
	\item no tabs expanded to spaces.
	\item no white space before opening braces.
	\item no white space after the word "if", "for", "while", etc.
	\item no braces around single-line blocks (e.g., if, for, and while bodies).
	\item integer-valued functions return -1 on error, 0 or positive on success.
	\item functions that return errors should set errstr(2).
	\item variable and function names are all lowercase, with no underscores.
	\item enum or \#defined constants should be Uppercase or UPPERCASE.
	\item struct tags are Uppercase, with matching typedefs.
	\item automatic variables (local variables inside a function) are never initialized at declaration.
	\item follow the standard idioms: use x$<$0 not 0$>$x, etc.
\end{itemize} The end they follow a very common development philosophy :
